---
title: "MyHealth Long Island Report"
author: "Steven P. Sanderson II, MPH - Data Scientist/IT Manager"
date: "Report Date: `r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document:
    code_folding: hide
    df_print: paged
    highlight: tango
    theme: flatly
    toc: yes
    toc_depth: 2
  pdf_document:
    toc: yes
    toc_depth: '2'
params:
  run_pt_reg_files:
    label: "Run Patient Registry Preprocessing Function:"
    value: "FALSE"
    input: select
    choices: [TRUE,FALSE]
  run_pt_rad_files:
    label: "Run Patient Radiology Preprocessing Function"
    value: "FALSE"
    input: select
    choices: [TRUE,FALSE]
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  # out.width = "100%",
  # out.height = "100%",
  dpi = 300
  )

# Lib Load ----------------------------------------------------------------

if(!require(pacman)) install.packages("pacman")
pacman::p_load(
    "odbc",
    "DBI",
    "tidyquant",
    "janitor",
    "tidyverse",
    "gt",
    "readxl",
    "lubridate"
)


# Source Functions --------------------------------------------------------

my_path <- "S:\\Global Finance\\1 REVENUE CYCLE\\Steve Sanderson II\\Code\\R\\MyHealth\\MyHealth_Referrals\\"
source_files <- list.files(my_path, "*.R")
load_files <- subset(
  source_files
  , subset = (
    !str_detect(source_files,"mhli_downstream_revenue.R") &
      !str_detect(source_files, "mhli_data_processing.R")
  )
)
map(paste0(my_path, load_files), source)

mhli_ds_tbl <- mhli_ds_query()
mhli_rad_tbl <- mhli_rad_ref_query()

run_pt_reg_files = params$run_pt_reg_files
run_pt_rad_files = params$run_pt_rad_files
mhli_pt_registry_data(.user_input = run_pt_reg_files)
mhli_pt_rad_data(.user_input = run_pt_rad_files)

```

# Report Informaiton

This report will produce the monthly downstream revenue for MyHealth Long Island patients and information on MyHealth Referrals. 

It is important to note that the MyHealth patient registry and referral files that are received do not contain the SSN of a patient or their associated hospital MRN, this means that a patient is match based upon the following:

1. Name
2. DOB and 
3. Biological Sex

We also filter out accounts that have $0.00 charges and those that start with a 2 or 1999 in order to only obtain true accounts. For radiology referrals we only take the first Rad appointment on or after the referral date provided. We define this as a patient type of U which is Outpatient Imaging Center.

There a total of `r scales::number(nrow(mhli_ds_tbl), big.mark = ",")` distinct records. The rad referrals file contains a total of `r scales::number(nrow(mhli_rad_tbl), big.mark = ",")`.

# Down Stream Revenue Data {.tabset .tabset-fade .tabset-pills}

## Down Stream by FC {.tabset .tabset-fade}
```{r mhli_ds_pvt_tbl}
mhli_pivot_tbl(.data = mhli_ds_tbl)
```

## Down Stream Summary {.tabset .tabset-fade}
```{r mhli_ds_summary_tbl}
mhli_ds_summary_tbl(.data = mhli_ds_tbl)
```

# Radiology Referral Data {.tabset .tabset-fade .tabset-pills}

## Down Stream by FC {.tabset .tabset-fade}
```{r mhli_rad_pvt_tbl}
mhli_rad_pvt_tbl(.data = mhli_rad_tbl)
```

## Down Stream Summary {.tabset .tabset-fade}
```{r mhli_rad_summary_tbl}
mhli_rad_summary_tbl(.data = mhli_rad_tbl)
```

## Counts by Facility and Provider {.tabset .tabset-fade}
```{r mhli_rad_facility_provider_count_tbl}
mhli_rad_facility_provider_count_tbl(.data = mhli_rad_tbl)
```

## Avg Lag from Referral Date {.tabset .tabset-fade}
```{r mhli_rad_ref_lag}
mhli_rad_ref_lag(.data = mhli_rad_tbl)
```

# Data Files

#### Down Stream Data
```{r ds_data_files}
write_csv(x = mhli_ds_tbl, "mhli_downstream_data.csv")
xfun::embed_file("mhli_downstream_data.csv")
````

#### Radiology Data
```{r rad_data_files}
write_csv(x = mhli_rad_tbl, "mhli_rad_data.csv")
xfun::embed_file("mhli_rad_data.csv")
````