---
title: "Friday Denials Report"
author: "Steven P. Sanderson II, MPH - Data Scientist/IT Manager"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    code_folding: hide
    highlight: tango
    theme: flatly
    toc: yes
  pdf_document:
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# Lib Load ----
if(!require(pacman)) install.packages("pacman")

pacman::p_load(
    "tidyverse"
    , "DBI"
    , "odbc"
    , "dbplyr"
    , "lubridate"
    , "janitor"
    , "knitr"
    , "kableExtra"
    , "tidyquant"
    , "ggrepel"
)

# DB Connection ----
db_con <- dbConnect(
    odbc(),
    Driver = "SQL Server",
    Server = "BMH-HIDB",
    Database = "SMSPHDSSS0X0",
    Trusted_Connection = T
)

# Data ----
query <- dbGetQuery(
    conn = db_con
    , paste0(
        "
        DECLARE @TODAY DATE;
        DECLARE @START DATE;
        DECLARE @END   DATE;
                
        SET @TODAY = GETDATE();
        SET @START = DATEADD(WK, DATEDIFF(WK, 0, @TODAY), - 3)
        SET @END   = DATEADD(DD, DATEDIFF(DD, 0, @TODAY), - 1);
        
        SELECT PAV.Med_Rec_No
        , PAV.PtNo_Num
        , PAV.Atn_Dr_No 
        , UPPER(PDV.PRACT_rpt_name) AS [Attending_Provider]
        , CASE
        	WHEN PDV.src_spclty_cd = 'HOSIM'
        		THEN 'HOSPITALIST'
        		ELSE 'PRIVATE'
          END AS [Hospitalist_Private]
        , PAV.hosp_svc
        , CAST(PAV.ADM_DATE AS DATE) AS [ADM_DATE]
        , CAST(PAV.DSCH_DATE AS DATE) AS [DSCH_DATE]
        , PAY.pay_cd
        , PAYCD.pay_cd_name
        , CAST(PAY.pay_entry_date AS DATE) AS [POST_DATE]
        , CAST(PAY.pay_date AS DATE) AS [DENIAL_DATE]
        , DATEDIFF(DAY, PAY.pay_date, PAY.pay_entry_date) AS [DENIAL_TO_ENTRY_LAG]
        , DATEDIFF(DAY, PAV.DSCH_DATE, PAY_ENTRY_DATE) AS [DSCH_TO_DENIAL_LAG]
        , PAV.tot_chg_amt
        , PAV.drg_no
        , PAV.drg_cost_weight
        , DRG.drg_med_surg_group
        , DRG.drg_complic_group
        , DRG.drg_name
        , DRG.drg_rate
        
        FROM SMSDSS.BMH_PLM_pTACCT_V AS PAV
        INNER JOIN SMSMIR.PAY AS PAY
        ON PAV.PT_NO = PAY.pt_id
        	AND PAV.unit_seq_no = PAY.unit_seq_no
        	AND PAV.from_file_ind = PAY.from_file_ind
        	AND PAY.pay_cd = '10501104'
        INNER JOIN SMSDSS.PAY_CD_DIM_V AS PAYCD
        ON PAY.pay_cd = PAYCD.pay_cd
        	AND PAY.orgz_cd = PAYCD.orgz_cd
        INNER JOIN SMSDSS.PRACT_DIM_V AS PDV
        ON PAV.Adm_Dr_No = PDV.src_pract_no
        	AND PAV.Regn_Hosp = PDV.orgz_cd
        LEFT OUTER JOIN SMSDSS.drg_v AS DRG
        ON CAST(PAV.Bl_Unit_Key AS VARCHAR) = CAST(SUBSTRING(DRG.bl_unit_key, 9, 20) AS varchar)
        	AND CAST(PAV.Pt_Key AS VARCHAR) = CAST(SUBSTRING(DRG.pt_key, 9, 20) AS VARCHAR)
        	AND CAST(PAV.drg_no AS VARCHAR) = CAST(DRG.drg_no AS VARCHAR)
        
        WHERE PAY.pay_entry_date >= @START
        AND PAY.pay_entry_date < @END

        "
    )
)

# Clean Names
df <- (
    query
    %>% as_tibble()
    %>% mutate(Attending_Provider = str_to_title(Attending_Provider))
    %>% mutate(Hospitalist_Private = str_to_title(Hospitalist_Private))
    %>% clean_names()
)

# DB Disconnect ----
dbDisconnect(db_con)

```

## Information about report

Data is pulled from DSS from the previous Friday through the close of business for the currently past Thursday.

For example if today is January 10th, 2020 then the data for records entered into FMS for dates of January 3rd, 2020 through January 9th, 2020 are pulled.

The encounter at that time must have a denial code of 10501104 which is defined as: REFERRED FOR APPEAL INITIAL

## Totals by Provider

```{r totals_by_provider, warning=FALSE, message=FALSE}
(
    df
    %>% select(
        attending_provider
        , hospitalist_private
        , tot_chg_amt
    )
    %>% group_by(attending_provider, hospitalist_private)
    %>% summarise(tot_chg_amt = sum(tot_chg_amt, na.rm = TRUE))
    %>% ungroup()
    %>% arrange(desc(tot_chg_amt))
    %>% adorn_totals()
    %>% mutate(tot_chg_amt = tot_chg_amt %>% scales::dollar())
    %>% set_names(
        "Attending"
        , "Hospitalist/Private"
        , "Total Charges"
    )
    %>% kable()
    %>% kable_styling(
        bootstrap_options = c(
            "striped"
            , "hover"
            , "condensed"
            , "responsive"
        )
        , font_size = 12
        , full_width = FALSE
    )
)
```

## Totals by Group
```{r total_by_group, warning=FALSE, message=FALSE}
(
    df
    %>% select(hospitalist_private, tot_chg_amt)
    %>% group_by(hospitalist_private)
    %>% summarise(tot_chg_amt = sum(tot_chg_amt, na.rm = TRUE))
    %>% ungroup()
    %>% arrange(hospitalist_private)
    %>% adorn_totals()
    %>% mutate(tot_chg_amt = tot_chg_amt %>% scales::dollar())
    %>% set_names("Hospitalist/Private","Total Charges")
    %>% kable()
    %>% kable_styling(
        bootstrap_options = c(
            "striped"
            , "hover"
            , "condensed"
            , "responsive"
        )
        , font_size = 12
        , full_width = FALSE
    )
)
```
## Chart of Totals by Group

```{r chart, message=FALSE, warning=FALSE}

(
  df
  %>% select(hospitalist_private, tot_chg_amt)
  %>% group_by(hospitalist_private)
  %>% summarise(tot_chg_amt = sum(tot_chg_amt, na.rm = TRUE))
  %>% ungroup()
  %>% mutate(tot_chg_txt = tot_chg_amt %>% scales::dollar())
  %>% mutate(prop_of_total = tot_chg_amt / sum(tot_chg_amt, na.rm = TRUE))
  %>% mutate(prop_of_total_txt = prop_of_total %>% scales::percent(accuracy = 0.02))
  %>% mutate(label_txt = str_glue("Total Charges: {tot_chg_txt}
                                  Proportion of Total: {prop_of_total_txt}"))
  %>% ggplot(
    mapping = aes(
      x = hospitalist_private
      , y = prop_of_total
    )
  ) +
    geom_col() +
    ggrepel::geom_label_repel(
      mapping = aes(
        label = label_txt
      )
      , direction = "y" 
    ) +
    labs(
      title = "Total Charges by Hospitalist/Private"
      , subtitle = "Denied Cases"
      , caption = "Percentages by group"
      , x = ""
      , y = "Proportion of Total Charges"
    ) +
    scale_y_continuous(labels = scales::percent_format(accuracy = 0.02)) +
    tidyquant::theme_tq() +
    tidyquant::scale_fill_tq()
)

```

## Data Download

Click on the link to get the full data: 
```{r, echo=FALSE, warning=FALSE, message=FALSE}

write.csv(df, "data.csv")
xfun::embed_file("data.csv")

```

