---
title: "Stony Brook Provider Practice Profile"
author: "Steven P. Sanderson II, MPH - Data Scientist/IT Manager"
date: "Report Date: `r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document:
    code_folding: hide
    df_print: paged
    highlight: tango
    theme: flatly
    toc: yes
    toc_depth: 2
  pdf_document:
    toc: yes
    toc_depth: '2'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  # out.width = "100%",
  # out.height = "100%",
  dpi = 300
  )

# Lib Load ----
if(!require(pacman)) install.packages("pacman")
pacman::p_load(
    "tidyverse"
    , "tidyquant"
    , "lubridate"
    , "R.utils"
    , "tibbletime"
    , "knitr"
    , "kableExtra"
    , "anomalize"
    , "DBI"
    , "odbc"
    , "dbplyr"
    , "readxl"
    , "gridExtra"
    , "patchwork"
    , "janitor"
)

# Source Functions ----
my_path <- ("S:\\Global Finance\\1 REVENUE CYCLE\\Steve Sanderson II\\Code\\R\\Functions\\SBU_Productivity\\")
source_files <- list.files(my_path, "*.R")
load_files <-  subset(
    source_files
    , subset = (
        str_starts(source_files, "sbu_")
    )
)
map(paste0(my_path, load_files), source)
```

# Information
The data for this report starts with encounters discharged from January 1st, 2018 forward.

# Case Counts {.tabset .tabset-fade .tabset-pills}

## Case Counts {.tabset .tabset-fade}

Case Counts.

### By Provider
```{r provider_pvt}
# By Provider
provider_case_type_pvt()
```

### By Division
```{r division_pvt}
# Counts by Division
division_case_type_count()
```

### By FC
```{r fc_pvt}
# Counts by FC
pyr_grp_count()
```

## Inpatient and Outpatient Counts {.tabset .tabset-fade}

Counts by inpatient and outpatient

### By Provider
```{r ip_op_counts_by_provider}
ip_op_counts_by_provider()
```

### By Division
```{r ip_op_counts_by_division}
ip_op_counts_by_division()
```

### By FC
```{r}
ip_op_counts_by_fc()
```

# Charges and Payments {.tabset .tabset-fade .tabset-pills}

Charges, Payments and Amounts Due

## By Provider
```{r chgs_pmts_by_provider}
chgs_pmts_by_provider()
```

## By Division
```{r chgs_pmts_by_division}
chgs_pmts_by_division()
```

## By FC
```{r chgs_pmts_by_fc}
chgs_pmts_by_fc()
```

# Profile Data {.tabset .tabset-fade .tabset-pills}

## SBU Practice Profile {.tabset .tabset-fade}

Myhealth Style Practice Profile Table

### By Provider
```{r myhealth_profile_by_provider}
myhealth_profile_by_provider()
```

### By Division
```{r myhealth_profile_by_division}
myhealth_profile_by_division()
```

### By FC
```{r myhealth_profile_by_fc}
myhealth_profile_by_fc()
```

## Profiles by Year {.tabset .tabset-fade}

Myhealth Style Practice Profile Table

### By Provider
```{r myhealth_profile_year_provider}
myhealth_profile_year_provider()
```

### By Division
```{r myhealth_profile_year_division}
myhealth_profile_year_division()
```

### By FC
```{r myhealth_profile_year_fc}
myhealth_profile_year_fc()
```

### By Year
```{r myhealth_profile_year}
myhealth_profile_year()
```

# Consult Data {.tabset .tabset-fade .tabset-pills}

Coded Consults by Discharge Year

## Totals {.tabset .tabset-fade}

### By Provider
```{r consults_by_provider}
consults_by_provider()
```

### By Division
```{r consults_by_division}
consults_by_division()
```

## Yearly {.tabset .tabset-fade}

### By Provider
```{r consults_by_provider_year}
consults_by_provider_year()
```

### By Division
```{r consults_by_division_year}
consults_by_division_year()
```

