---
title: "OPPE Report"
author: "Steven P. Sanderson II, MPH - Data Scientist/IT Manager"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    code_folding: show
    highlight: tango
    theme: flatly
    toc: yes
  pdf_document:
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# Lib Load ----
if(!require(pacman)) install.packages("pacman")
pacman::p_load(
    "tidyverse"
    , "tidyquant"
    , "lubridate"
    , "R.utils"
    , "tibbletime"
    , "knitr"
    , "kableExtra"
    , "anomalize"
    , "DBI"
    , "odbc"
    , "dbplyr"
    , "readxl"
)

# Source Functions ----
my_path <- ("S:\\Global Finance\\1 REVENUE CYCLE\\Steve Sanderson II\\Code\\R\\Functions\\")
source_files <- list.files(my_path, "*.R")
load_files <-  subset(
    source_files
    , subset = (
        str_detect(source_files, "oppe_") | 
            str_detect(source_files, "clean")
    )
)
map(paste0(my_path, load_files), source)

# DB Connection ----
db_con <- dbConnect(
    odbc(),
    Driver = "SQL Server",
    Server = "BMH-HIDB",
    Database = "SMSPHDSSS0X0",
    Trusted_Connection = T
)

# Report Parameters ----
# Dates
alos_start_date <- Sys.Date() %m-% months(18) %>%
    floor_date(unit = "months")
alos_end_date <- Sys.Date() %>%
    floor_date(unit = "months")

# Provider
provider_id = '017863'

# Tables ----
# Provider tbl ----
provider_tbl <- tbl(
    db_con,
    in_schema(
        schema = "smsdss"
        , table = "pract_dim_v"
    )
) %>%
    filter(
        orgz_cd == 'S0X0'
        , src_pract_no == provider_id
    ) %>%
    as_tibble() %>%
    select(
        src_pract_no
        , pract_rpt_name
        , src_spclty_cd
        , orgz_cd
        , med_staff_dept
    ) %>%
    mutate(
        pract_rpt_name = str_to_title(pract_rpt_name)
    ) %>%
    clean_names()

# ALOS Tables ----
alos_svc_line_tbl <- tbl(
    db_con,
    in_schema(
        schema = "smsdss"
        , table = "c_LIHN_Svc_Line_tbl "
    )
) %>%
    as_tibble() %>%
    clean_names()

alos_pav_tbl <- tbl(
    db_con,
    in_schema(
        schema = "smsdss"
        , table = "BMH_PLM_PtAcct_V"
    )
) %>%
    filter(
        Dsch_Date >= alos_start_date
        , Dsch_date < alos_end_date
        , Plm_Pt_Acct_Type == "I"
        , tot_chg_amt > 0
        , str_sub(PtNo_Num %>% as.character(), 1, 1) != '2'
        , str_sub(PtNo_Num %>% as.character(), 1, 4) != '1999'
        , !is.na(drg_no)
        , !drg_no %in% c(
            '0','981','982','983','984','985',
            '986','987','988','989','998','999'
        )
        , Atn_Dr_No == provider_id
    ) %>%
    select(
        Med_Rec_No
        , Pt_No
        , PtNo_Num
        , Adm_Date
        , Dsch_Date
        , Days_Stay
        , Atn_Dr_No
        , drg_no
        , drg_cost_weight
        , Regn_Hosp
        , Pyr1_Co_Plan_Cd
    ) %>%
    mutate(
        Dsch_Month = month(Dsch_Date)
        , Dsch_Yr = year(Dsch_Date)
        , LOS = if_else(
            Days_Stay == '0'
            , '1'
            , Days_Stay
        )
    ) %>%
    as_tibble()

alos_pav_tbl <- alos_pav_tbl %>%
    mutate(
        PtNo_Num = PtNo_Num %>% as.character()
        , Pt_No = Pt_No %>% str_squish()
    ) %>%
    clean_names()

alos_aprdrg_tbl <- tbl(
    db_con,
    in_schema(
        schema = "Customer"
        , table = "Custom_DRG"
    )
) %>%
    select(
        `PATIENT#`
        , APRDRGNO
        , SEVERITY_OF_ILLNESS
    ) %>%
    as_tibble() %>%
    rename(Encounter = `PATIENT#`) %>%
    mutate(Encounter = Encounter %>% str_squish()) %>%
    clean_names()

alos_bench_tbl <- tbl(
    db_con,
    in_schema(
        schema = "smsdss"
        , table = "c_LIHN_SPARCS_BenchmarkRates"
    )
) %>%
    filter(
        `Measure ID` == '4'
        , `Benchmark ID` == '3'
    ) %>%
    as_tibble() %>%
    clean_names()

alos_outlier_tbl <- tbl(
    db_con,
    in_schema(
        schema = "smsdss"
        , table = "c_LIHN_APR_DRG_OutlierThresholds"
    )
) %>%
    as_tibble() %>%
    clean_names()

alos_pyr_dim_tbl <- tbl(
    db_con,
    in_schema(
        schema = "smsdss"
        , table = "pyr_dim_v"
    )
) %>%
    as_tibble() %>%
    select(
        pyr_cd
        , orgz_cd
        , pyr_group2
    ) %>%
    clean_names()

alos_vst_rpt_tbl <- tbl(
    db_con,
    in_schema(
        schema = "smsmir"
        , table = "vst_rpt"
    )
) %>%
    filter(
        vst_end_date >= alos_start_date
        , vst_end_date < alos_end_date
        , vst_type_cd == "I"
    ) %>%
    select(
        pt_id
        , ward_cd
    ) %>%
    as_tibble() %>%
    mutate(pt_id = pt_id %>% str_squish()) %>%
    clean_names()

# Final ALOS Table
alos_tbl <- alos_svc_line_tbl %>%
    # joins
    inner_join(
        alos_pav_tbl
        , by = c("encounter" = "pt_no")
        , keep = T
    ) %>%
    left_join(
        alos_aprdrg_tbl
        , by = c("pt_no_num" = "encounter")
        , keep = T
    ) %>%
    left_join (
        alos_bench_tbl
        , by = c(
            "lihn_svc_line" = "lihn_service_line"
            , "aprdrgno" = "aprdrg_code"
            , "severity_of_illness" = "soi"
        )
        , keep = T
    ) %>%
    left_join(
        provider_tbl
        , by = c(
            "atn_dr_no" = "src_pract_no"
            , "regn_hosp" = "orgz_cd"
        )
        , keep = T
    ) %>%
    left_join(
        alos_outlier_tbl
        , by = c("aprdrgno" = "apr_minus_drg_code")
        , keep = T
    ) %>%
    left_join(
        alos_pyr_dim_tbl
        , by = c(
            "pyr1_co_plan_cd" = "pyr_cd"
            , "regn_hosp" = "orgz_cd"
        )
        , keep = T
    ) %>%
    left_join(
        alos_vst_rpt_tbl
        , by = c("encounter" = "pt_id")
        , keep = T
    ) %>%
    # select statement
    select(
        med_rec_no
        , encounter
        , pt_no_num
        , adm_date
        , dsch_date
        , dsch_month
        , dsch_yr
        , days_stay
        , atn_dr_no
        , pract_rpt_name
        , drg_no
        , lihn_svc_line
        , src_spclty_cd
        , aprdrgno
        , severity_of_illness
        , performance
        , outlier_threshold
        , drg_cost_weight
        , pyr_group2
        , med_staff_dept
        , ward_cd
    ) %>%
    # mutate statements
    mutate(
        los = if_else(
            days_stay == 0
            , 1.0
            , days_stay
        )
        , hosim = if_else(
            src_spclty_cd == 'HOSIM'
            , "Hospitalist"
            , "Private"
        )
        , performance = case_when(
            performance == 0 ~ 1.0
            , (is.na(performance) & los == 0) ~ 1.0
            , (is.na(performance) & los != 0) ~ (los %>% as.numeric())
            , T ~ performance
        )
        , outlier_flag = if_else(
            los > outlier_threshold
            , 1
            , 0
        )
        , case_var = round((los - performance), 4)
        , case_index = round(los / performance, 4)
        , los_sd = sd(los)
        , z_minus_score = round((los - performance) / los_sd, 4)
        , zscore_ul = 1.96
        , zscore_ll = -1.96
        , last_rpt_month = if_else(
            dsch_month < 10
            , str_c(dsch_yr, 0, dsch_month)
            , str_c(dsch_yr, dsch_month)
        )
        , proper_name = str_to_title(pract_rpt_name)
    ) %>%
    as_tbl_time(index = dsch_date) %>%
    arrange(dsch_date)

# Readmit Tables ----
ra_detail_tbl <- tbl(
    db_con,
    in_schema(
        schema = "smsdss"
        , table = "C_READMIT_DASHBOARD_DETAIL_TBL"
    )
) %>%
    as_tibble() %>%
    mutate(
        dsch_bench_yr = (Dsch_YR - 1) %>% as.character()
        , SEVERITY_OF_ILLNESS = SEVERITY_OF_ILLNESS %>% as.character()
    ) %>%
    clean_names()

ra_bench_tbl <- tbl(
    db_con,
    in_schema(
        schema = "smsdss"
        , table = "c_Readmit_Dashboard_Bench_Tbl"
    )
) %>%
    as_tibble() %>%
    filter(!is.na(SOI)) %>%
    mutate(
        SOI = SOI %>% as.character()
    ) %>%
    clean_names()

ra_vst_tbl <- tbl(
    db_con,
    in_schema(
        schema = "smsmir"
        , table = "vst_rpt"
    )
) %>%
    filter(
        vst_type_cd == "I"
    ) %>%
    select(
        pt_id
        , ward_cd
    ) %>%
    as_tibble() %>%
    mutate(
        pt_id = pt_id %>% str_squish()
        , episode_no = str_sub(pt_id, 5)
    ) %>%
    filter(!is.na(ward_cd)) %>%
    clean_names()

# Final RA Table
readmit_tbl <- ra_detail_tbl %>%
    left_join(
        ra_bench_tbl
        , by = c(
            "lihn_svc_line" = "lihn_svc_line"
            , "dsch_bench_yr" = "bench_yr"
            , "severity_of_illness" = "soi"
        )
    ) %>%
    left_join(
        ra_vst_tbl
        , by = c("pt_no_num" = "episode_no")
    ) %>%
    mutate(
        adm_date = ymd(adm_date)
        , dsch_date = ymd(dsch_date)
        , pt_count = 1
        , bench_yr = dsch_bench_yr
        , ra_sd = sd(ra_flag)
        , z_minus_score = round(
            (ra_flag - readmit_rate) / ra_sd, 4
        )
        , severity_of_illness = severity_of_illness %>%
            as.numeric()
        , proper_name =  str_to_title(pract_rpt_name)
    ) %>%
    select(
        med_rec_no
        , pt_no_num
        , adm_date
        , dsch_date
        , payor_category
        , atn_dr_no
        , pract_rpt_name
        , proper_name
        , med_staff_dept
        , lihn_svc_line
        , severity_of_illness
        , dsch_yr
        , dsch_month
        , dsch_day_name
        , dsch_disp
        , dsch_disp_desc
        , drg_cost_weight
        , hospitalist_private
        , los
        , interim
        , pt_count
        , ra_flag
        , bench_yr
        , readmit_rate
        , ra_sd
        , z_minus_score
        , ward_cd
    ) %>%
    rename(
        readmit_rate_bench = readmit_rate
        , readmit_count = ra_flag
    ) %>%
    filter(atn_dr_no == provider_id) %>%
    as_tbl_time(index = dsch_date) %>%
    arrange(dsch_date)

# CPOE Tables ----
cpoe_detail_tbl <- tbl(
    db_con,
    in_schema(
        schema = "smsdss"
        , table = "c_CPOE_Rpt_Tbl_Rollup_v"
    )
) %>%
    select(
        req_pty_cd
        , Hospitalist_Np_Pa_Flag
        , Ord_Type_Abbr
        , Unknown
        , Telephone
        , `Per RT Protocol`
        , Communication
        , `Specimen Collect`
        , `Specimen Redraw`
        , CPOE
        , `Nursing Order`
        , Written
        , `Verbal Order`
        , ent_date
    ) %>%
    as_tibble() %>%
    clean_names() %>%
    mutate(ent_date = ymd(ent_date)) %>%
    filter(req_pty_cd == provider_id) %>%
    as_tbl_time(index = ent_date) %>%
    arrange(ent_date)

cpoe_tbl <- cpoe_detail_tbl %>%
    left_join(
        provider_tbl
        , by = c(
            "req_pty_cd" = "src_pract_no"
        )
    ) %>% 
    filter(orgz_cd == "S0X0") %>%
    mutate(
        proper_name = str_to_title(pract_rpt_name)
        , total_orders = 
            unknown +
            telephone +
            per_rt_protocol +
            communication +
            specimen_collect +
            specimen_redraw +
            cpoe +
            nursing_order +
            written +
            verbal_order
    )

# Denials Tables ----
denials_tbl <- dbGetQuery(
    db_con
    , paste0("
    DECLARE @TODAY DATE;
DECLARE @START DATE;
DECLARE @END   DATE;

SET @TODAY = CAST(GETDATE() AS date);
SET @START = DATEADD(YY, DATEDIFF(YY, 0, @TODAY) - 5, 0);
SET @END   = DATEADD(MM, DATEDIFF(MM, 0, @TODAY), 0);

SELECT PAV.Med_Rec_No,
	PAV.PtNo_Num,
	CAST(PAV.ADM_DATE AS DATE) AS [Adm_Date],
	CAST(PAV.Dsch_Date AS DATE) AS [Dsch_Date],
	CAST(PAV.DAYS_STAY AS INT) AS [Days_Stay],
	PAV.drg_no,
	DRG.drg_name,
	PAV.drg_cost_weight,
	PAV.Atn_Dr_No,
	PDV.pract_rpt_name,
	CASE 
		WHEN PAV.Plm_Pt_Acct_Type != 'I'
			THEN LIHNOP.LIHN_Svc_Line
		ELSE LIHNIP.LIHN_Svc_Line
		END AS [Svc_Line],
	CASE 
		WHEN DENIALS.pt_no IS NOT NULL
			THEN 1
		ELSE 0
		END AS [Denial_Flag],
	DENIALS.UM_Days_Denied,
	DENIALS.Dollars_Appealed,
	DENIALS.Dollars_Recovered,
	PAV.tot_chg_amt,
    PAV.Plm_Pt_Acct_Type
FROM SMSDSS.BMH_PLM_PtAcct_V AS PAV
INNER JOIN SMSDSS.pract_dim_v AS PDV ON PAV.Atn_Dr_No = PDV.src_pract_no
	AND PAV.Regn_Hosp = PDV.orgz_cd
LEFT OUTER JOIN SMSDSS.drg_dim_v AS DRG ON PAV.DRG_NO = DRG.DRG_NO
	AND DRG.drg_vers = 'MS-V25'
LEFT OUTER JOIN SMSDSS.c_LIHN_Svc_Line_Tbl AS LIHNIP ON PAV.PtNo_Num = LIHNIP.Encounter
LEFT OUTER JOIN SMSDSS.c_LIHN_OP_Svc_Line_Tbl AS LIHNOP ON PAV.PtNo_Num = LIHNOP.Encounter
LEFT OUTER JOIN (
	SELECT CAST(rtrim(ltrim('0000' + CAST(a.bill_no AS CHAR(13)))) AS CHAR(13)) COLLATE SQL_LATIN1_GENERAL_PREF_CP1_CI_AS AS [Pt_No],
		e.appl_dollars_appealed AS [Dollars_Appealed],
		e.appl_dollars_recovered AS [Dollars_Recovered],
		d.rvw_Dys_dnd AS [UM_Days_Denied]
	FROM [BMH-3MHIS-DB].MMM_COR_BMH_LIVE.dbo.visit_view AS a
	LEFT JOIN [BMH-3MHIS-DB].MMM_COR_BMH_LIVE.dbo.CTC_VISIT AS b ON a.visit_id = b._fk_visit
	LEFT JOIN [BMH-3MHIS-DB].MMM_COR_BMH_LIVE.dbo.CTC_INSURANCE AS c ON a.visit_id = c._fk_visit
	LEFT JOIN [BMH-3MHIS-DB].[MMM_COR_BMH_LIVE].[dbo].[CTC_UM_Denial] AS d ON c._pk = d._fk_insurance
	LEFT OUTER JOIN [BMH-3MHIS-DB].MMM_COR_BMH_LIVE.dbo.CTC_UM_APPEAL AS e ON d._pk = e._fk_UM_Denial
	WHERE E.APPL_doLLARS_APPEALED IS NOT NULL
	) AS DENIALS ON PAV.Pt_NO = DENIALS.Pt_No
WHERE Adm_Date >= @START
	AND Adm_Date < @END
	AND PAV.tot_chg_amt > 0
	AND LEFT(PAV.PTNO_NUM, 1) != '2'
	AND LEFT(PAV.PTNO_NUM, 4) != '1999'
	AND PAV.Atn_Dr_No = '", provider_id ,"'
	AND (
		(
			PAV.Plm_Pt_Acct_Type = 'I'
			AND PAV.drg_no IS NOT NULL
			)
		OR (
			PAV.Plm_Pt_Acct_Type != 'I'
			AND PAV.drg_no IS NULL
			)
		)
ORDER BY PAV.Plm_Pt_Acct_Type,
	PAV.Adm_Date
    ")
)

# Final Denials Table
denials_tbl <- denials_tbl %>%
    clean_names() %>%
    mutate(
        adm_date = adm_date %>% ymd()
        , dsch_date = dsch_date %>% ymd()
    ) %>%
    as_tbl_time(index = adm_date) %>%
    arrange(adm_date)

# Disconnect DB ----
dbDisconnect(db_con)

# DRG Exclude ----
drg_exclude <- read_xlsx("G:\\R Studio Projects\\Credentialing_CPOE\\drg_exclude.xlsx") %>%
    clean_names()
# APR DRG Thresholds ----
apr_drg_thresholds_tbl <- read_xlsx("G:\\R Studio Projects\\Credentialing_CPOE\\apr_drg_thresholds.xlsx") %>%
    clean_names()
# APR DRG Exclude ----
apr_drg_exclude <- read_xlsx("G:\\R Studio Projects\\Credentialing_CPOE\\ra_apr_drg_exclude.xlsx") %>%
    clean_names()
```

# Information About Report

This report gives information on a providers performance in regards to a few things. The items this report covers are:

* Average Lengh of Stay
    + History with Linear Trend
    + Z-Score with Linear Trend
    + CMI and SOI with Linear Trend
    + Excess days from Benchmark
    + Excess Days Anomaly Analysis
    + Outliers are excluded, see [Appendix]
* Readmissions
    + History with Linear Trend
    + Z-Score with Linear Trend
    + CMI and SOI with Linear Trend
    + Excess Rate from Benchmark
    + Excess Readmit Rate Anomaly Analysis
    
Important note about ALOS Data:

* The inpatient account must have positive total charges on it
* The following Medical Staff Departments are excluded:
    + Anesthesiology
    + Emergency Department
    + Pathology

The following MS-DRG numbers are excluded:

```{r drg_exclude_tbl, echo=FALSE}
drg_exclude  %>%
    kable() %>%
    kable_styling(bootstrap_options = c(
        "striped"
        , "hover"
        , "condensed"
        , "responsive"
        )
        , font_size = 12
        , full_width = F
    )
```

Import note about Readmit Data:

* Only discharge dispositions of AHR and ATW (Home & Home - Adult Home - Assisted Living) are included
* Certain APR-DRG's are excluded, see [Appendix]

# Data Exploration

#### Discharges and ALOS data
```{r discharges_and_alos_by_provider, echo=FALSE}
alos_tbl %>%
    select(
        proper_name
        , los
        , performance
        ) %>%
    group_by(proper_name) %>%
    summarize(
        Total_Discharges = n()
        , ALOS = round(mean(los), 2)
        , ELOS = round(mean(performance), 2)
        , Excess = (ALOS - ELOS)
    ) %>%
    ungroup() %>%
    set_names(
        c(
            "Provider"
            , "Total Discharges"
            , "ALOS"
            , "ELOS"
            , "Excess"
        )
    )  %>%
    kable() %>%
    kable_styling(bootstrap_options = c(
        "striped"
        , "hover"
        , "condensed"
        , "responsive"
        )
        , font_size = 12
        , full_width = F
        , position = "left"
    ) 
```

#### Discharges and Readmit Rate data
```{r discharges_and_readmit_rate_by_provider, echo=FALSE}
readmit_tbl %>%
    select(
        proper_name
        , pt_count
        , readmit_count
        , readmit_rate_bench
        , interim
        , los
    ) %>%
    group_by(proper_name) %>%
    summarize(
        Total_Discharges = sum(pt_count)
        , rr = round((sum(readmit_count) / Total_Discharges), 4)
        , perf = round(mean(readmit_rate_bench), 4)
        , Excess = (rr - perf)
        , interim = round(mean(interim, na.rm = T), 2)
        , alos = round(mean(los), 2)
        , rr_text = scales::percent(rr)
        , perf_text = scales::percent(perf)
        , excess_text = scales::percent(Excess)
    ) %>%
    ungroup() %>%
    set_names(
        c(
            "Provider"
            , "Total Discharges"
            , "Readmit Rate"
            , "Expected Rate"
            , "Excess Readmit Rate"
            , "Mean Days to Readmit"
            , "ALOS"
            , "Readmit Rate %"
            , "Expected Rate %"
            , "Excess Rate %"
        )
    ) %>%
    select(
        Provider
        , "Total Discharges"
        , "Readmit Rate %"
        , "Expected Rate %"
        , "Excess Rate %"
        , "ALOS"
        , "Mean Days to Readmit"
    ) %>%
    kable() %>%
    kable_styling(bootstrap_options = c(
        "striped"
        , "hover"
        , "condensed"
        , "responsive"
        )
        , font_size = 12
        , full_width = F
        , position = "left"
    )
```
#### Denial Data

Denial data is gathered by a patients admit date. The data is gathered from today minus 5 years, starting on the first of the year. For example if today is 2019-11-05 then the start date is 2014-01-01.

```{r denial_tbl, echo = FALSE}
denials_tbl %>%
    select(
        pt_no_num
        , adm_date
        , days_stay
        , denial_flag
        , um_days_denied
        , dollars_appealed
        , dollars_recovered
        , tot_chg_amt
        , plm_pt_acct_type
    ) %>%
    group_by(plm_pt_acct_type) %>%
    summarize(
        tot_admits = n()
        , tot_denials = sum(denial_flag)
        , alos = round(mean(days_stay), 2)
        , avg_denied_days = case_when(
          is.nan(round(mean(um_days_denied, na.rm = T), 2))
          ~ 0
          , TRUE ~ round(mean(um_days_denied, na.rm = T), 2)
        )
        , tot_dollars_denied = sum(dollars_appealed, na.rm = T)
        , tot_dollars_recoverd = sum(dollars_recovered, na.rm = T)
        , tot_chgs = sum(tot_chg_amt)
        , denial_pct = (tot_denials / tot_admits)
        , denial_dollar_pct = (
            sum(dollars_appealed, na.rm = T) / sum(tot_chg_amt, na.rm = T)
        )
        , recovery_pct = case_when(
          is.nan(tot_dollars_recoverd / tot_dollars_denied) ~ 0
          , TRUE ~ (tot_dollars_recoverd / tot_dollars_denied)
        ) #(tot_dollars_recoverd / tot_dollars_denied)
    ) %>%
    mutate(
        tot_dollars_denied = tot_dollars_denied %>% scales::dollar()
        , tot_dollars_recoverd = tot_dollars_recoverd %>% scales::dollar()
        , tot_chgs = tot_chgs %>% scales::dollar()
        , denial_pct = denial_pct %>% scales::percent()
        , denial_dollar_pct = denial_dollar_pct %>% scales::percent()
        , recovery_pct = recovery_pct %>% scales::percent()
    ) %>%
    ungroup() %>%
    set_names(
        "IP/OP"
        , "Admits"
        , "Denials"
        , "ALOS"
        , "Avg Days Denied"
        , "Dollars Denied"
        , "Dollars Recovered"
        , "Total Charges"
        , "% Cases Denied"
        , "% Dollars Denied"
        , "% Recovered"
    ) %>%
    kable() %>%
    kable_styling(
        bootstrap_options = c(
            "striped"
            , "hover"
            , "condensed"
            , "responsive"
            )
        , font_size = 12
        , full_width = T
        , position = "left"
    ) 
```

# CPOE Order Plots

```{r oppe_plot, echo=FALSE, message=FALSE,warning=FALSE}
# Viz ----
oppe_cpoe_plot(cpoe_tbl)
```

# Length of Stay Trends

```{r alos_trend_tbl, echo=FALSE, message=FALSE, warning=FALSE}
oppe_alos_plot(alos_tbl)
```

# Readmission Trends

```{r readmit_trend_tbl, echo=FALSE, message=FALSE, warning=FALSE}
oppe_readmit_plot(readmit_tbl)
```

# Gartner Magic Chart

Shows data collapsed by week. Excess Readmit Rate on the y axis and Excess LOS on the x axis. A provider wants to be in the lower left quadrant where both x and y are negative.

```{r gartner_magic_chart, echo=FALSE, message=FALSE, warning=FALSE}
oppe_gartner_magic_plot()
```

# Denials

```{r denials_plts, echo=FALSE, message=FALSE, warning=FALSE}
oppe_denials_plot()
```

# Appendix

#### APR-DRG thresholds

<details>
<summary>Click to see APR-DRG Thresholds</summary>
```{r apr_drg_thresholds, echo=FALSE, message=FALSE, warning=FALSE}
apr_drg_thresholds_tbl %>%
  set_names("APR DRG","Description","Threshold") %>%
  kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), font_size = 12)
```
</details>
</p>

<details>
<summary>Click to see APR-DRG Exclusions for Readmits</summary>
```{r apr_drg_exclude, echo=FALSE, message=FALSE, warning=FALSE}
apr_drg_exclude %>%
    set_names("APR DRG","Description") %>%
    kable() %>%
    kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), font_size = 12)
```
</details>

```{r clear_env, echo=FALSE, message=FALSE, warning=FALSE}
rm(list = ls())
```